Asymmetric Agents and their Willingness to Fight\\ Customer Loyalty and its Impact on Competition

### 2015-10-18 Paper1.tex
Example Uniform
Added small section on the implications of having a uniform distribution

>>>>

\section{Examples}
\subsection{Basic Case - Uniform Distribution}
First consider the basic case of a uniform distribution of customers. Thus $g(\theta)\equiv\tilde{g}$ and $g'(\cdot)=0$. The solutions to the firms problem become:

\begin{align}
x_1^C &= \tilde{g}\frac{\gamma_1}{c_1} + G(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\\
x_2^C &= \tilde{g}\frac{\gamma_2}{c_2} + \big(1-G(x_1-x_2)\big)\frac{\partial \gamma_2}{\partial x_2}\frac{1}{c_2}
\end{align}

The reaction function equals:
\begin{align*}
\frac{\d x_1}{\d x_2} &= A_i^{-1} \left( -\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
A_i &= 1 -\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\gamma}{c_1}
\end{align*}

If the efforts don't affect the value extraction of the firms, the optimal efforts of the firms are given by $\tilde{g}\frac{\gamma_i}{c_i}$ and thus proportional to the value and the cost ratio. Furthermore, the efforts are independent of the competitors efforts.

If the firm also derive value from the efforts then the reaction is always negative. A higher effort by firm $2$ leads to a lower market share of firm $1$, which reduces its incentives to exert efforts.
